\documentclass[a4paper]{article}
\usepackage{lineno}
\title{Cover Letter}
\author{Irakli Chakaberia\\
Kansas State University}
\date{\today}

\setlength{\topmargin}{-15mm}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-8mm}
\setlength{\textheight}{9in}
\setlength{\footskip}{1in}
\setlength{\parindent}{0in}

\begin{document}
\pagestyle{empty}
%\linenumbers
\fontsize{12}{15}
\selectfont
\maketitle
\thispagestyle{empty}

\textbf{Postdoctoral Research Associate - Experimental Particle Physics//
Job Code: P-EPP1//
Department: Particle Physics Division (PPD)
}

Dear Dr. David Christian,
\\
\\
I am a PhD student in the last phase of my studies. I am very interested in postdoctoral research associate position in experimental particle physics at Fermilab.
My current research is in high energy physics with CMS experiment. It would be a tremendous opportunity to continue research in particle physics at Fermilab.
\\
\\
Please consider my application for the post-doctoral position.
Below is the list of referees you are welcome to contact for recommendations:
\begin{itemize}
\item \textbf{Dr. Tim Bolton}\\
Professor, Principle Investigator\\
Kansas State University
\begin{description}
\item{Address:} 43A C ardwell Hall\\
Kansas State University\\
Manhattan, KS, USA, 66506
\end{description}
\textbf{Email:} bolton@phys.ksu.edu\\
\textbf{Tel:} +17855321664\\

\item \textbf{Dr. Danek Kotlinski}\\
Senior Scientist, Principle Investigator of CMS Pixel Detector Group\\
Paul Scherrer Institute\\
\textbf{Address:} Paul Scherrer Institut\\
OFLC /004\\
Villigen, Switzerland, CH-5232\\
\textbf{Email:} danek.kotlinski@psi.ch\\
\textbf{Tel:} +41562845020\\

\item \textbf{Dr. Kaori Maeshima}\\
Scientist at FNAL, Group Leader of Web-Based Monitoring Team of CMS\\
Fermi National Accelerator Laboratory\\
\textbf{Address:} Fermilab, MS205\\
PO BOX 500\\
Batavia, IL, USA, 60510\\
\textbf{Email:} maeshima@fnal.gov\\
\textbf{Tel:} +16308403917\\
\end{itemize}



Please, find attached application documents:
\begin{itemize}
\item Curriculum Vitae
\item List of Publications
\item Statement of Research
\end{itemize}



I look forward to hearing from you. Please feel free to contact me if you need any additional information.
\\
\\
\\
\\
Sincerely,\\
\\
Irakli Chakaberia\\
\texttt{E-mail:irakli@phys.ksu.edu}\\
Tel: 785 317 7881\\

\end{document}
