%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%



%-------------------------------------------------------------------------------
\input{header.tex}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
 {Company Recruitment Team}
 {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Motivation Letter for PhD Application}
% How the letter is opened
\letteropening{Dear Dr. Matthew Charles}
\newcommand{\thesis}{Recherche de nouvelle physique dans des désintégrations de mésons beaux en trois corps sans particule charmée avec l’expérience LHCb}

% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
%\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed

% Print the title with above letter informations
\makelettertitle




%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
I am writing this letter to express my strong interest in the Ph.D. position : "\thesis"

\lettersection{About me}

I graduated last year with a Master's degree in "high energy and computational physics" from Cadi Ayyad University in Morocco. Pursuing my Ph.D. with experts and doing research on the latest topics of physics is my childhood dream.

I feel comfortable processing several challenging things at once. This ability helps me to be successful in my study (First in my class of master degree) and acquire extra-curricular knowledge in the computer science field (about 5 years of experience with programming)


My current research interests are in supervised and unsupervised machine learning in high energy physics.It took me a long journey during my career before I came to this well-defined area of interest. It started in the second year of my Physics B.Sc. During that time, like every student, I had a vague interest in high energy physics. I did not know yet if this interest was more theoretical or experimental. Nevertheless, After Google’sAlphaGo became the first Computer Go program to beat an unhandicapped professional human player, I started to learn about machine learning and applied it in many physics and no physics problems.


Since I was in college until now, I have joined several online classes related to computer science such as web programming, Linux, data science, data structures and algorithms, probability and statistics, linear algebra, Python, and so on.

I realize my shortcomings in the field of data science, that's why I want to pursue my master's degree to excel it.

I did not only take online classes, but in 2019, I also took offline classes held by Digital Talent Scholarship for the Fresh Graduate Academy in the field of big data analytics where there was an online test for the selection stage.


please visit my website for more information about me

\lettersection{Why this thesis?}
After working in the data analysis area for more than 4 years, I have acquired huge experience in many aspects of these jobs. It gives me a big picture of machine learning and AI should be able to help within the business, such as predicting sales trends, using statistics to predict customer annuity trends of each year, or using it with ETL in the payment process with real-time machine learning.


combine two of my favorite subjects ....


i ussaly wonder why the use of dnn in hep



good reputation of CEA 
I think LPNHE can help me with this ambition since it has a strong LHCb group with access to formidable computational resources, also I can adapt quickly to new scenarios and computational challenges in the LHCb experiment now and after the upgrade, 
\lettersection{Why me}
website page

new challenges, and thinking about innovative ways to tackle them are a great motivation for me.

 see my work


With my educational background and experiences, I believe that I am a suitable candidate for this program. This master's program can develop my creative thinking skills and my ability to confront contemporary challenges. It also aimed to provide students with real industry Data Science skills, namely from defining a business problem to presenting the work results, solution implementation and reporting. I need those skills because they are very prominent parts to be a professional data scientist. I have some subjects that I want to study at Innopolis University such as Machine Learning, Big Data, and High-Dimensional Data Analysis.



 My project at (Company A) focused on tracking car buyers whether they have visited the service center to check the car condition as scheduled or not and analyze potential customers who may come back to buy the car again. I also worked closely with the sales department to predict what future sales prospects will be. After that, at (Company B), I had to study ways to keep overdue tracking customers and analyze a person's behavior so that I was able to assess which debtors were likely to fail to pay the debt on schedule. Therefore, I would like to study how to use machine learning for preprocessing and use real-time data and business reports through automated ETL processes. Furthermore, with the SAS BI project, I joined to analysis of variance and models which was used to relate the factors considered, analyze the differences among the different user requirements and finally perform on the dashboard


I strongly believe that a Master in Data Science, with focus on Advanced Machine Learning and Special Topic in Regression, would certainly be valuable in allowing me to catch my goals. At the same time, it would also let me to engage my conceptual and quantitative experiences in analyzing complex business problems, beginning new ways in research. With (Researcher name)'s research in ‘Machine Learning for Extreme Event Detection’. I would also like to study how the future climate in the Asia Pacific region will change as a result of global warming. I wanted to predict the critical damage locations, and data streams using machine learning approaches. I expect this research to be able to calculate storm paths, determine the duration of storms most frequently to strike, and use machine learning techniques to find out where the storm is most likely to have a major impact around the Asia Pacific.

With these experiences, I am satisfied I can provide the best assistance to your research area. Moreover, the reputation of high-quality education standards and faculty members are the main factors that have encouraged me to apply for this scholarship. Finally, I desire to catch up on my dream to be a professional in data analyst that will benefit many people. Completing this degree should provide the experience for me to achieve my aspirations.



Besides my thorough theoretical knowledge got during my master in high energy and computational physics, I also possess strong numerical and data analysis skills obtained during multiple research projects, also I have a lot of experience in programming languages (Python and C++) and frameworks (ROOT, DaVinci ..), and I have a strong desire for professional development. I believe that my diligence, my practical research experience, and organizing abilities, high enthusiasm, and interest in experimental particle physics are most conducive to make me an ideal candidate for this Ph.D.

After completing my Ph.D., I plan to pursue a postdoc likely in the area of applied new technologies like machine learning in data analysis of the LHCb experiment. Driven by a lifelong interest in experimental particle physics, I am keen to continue my education in this subject and to perform my own research which can contribute to the knowledge of the field.

I am available immediately to start an internship before the beginning of the PhD, and please find in my CV attached a list of referees you are welcome to contact for recommendations

I will gladly answer questions you may have and hope to hear from you soon. Sincerely,

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
